---
title: "Merge Assignee, Location, and Patent Tables"
output: html_document
---
#### Note: This HTML document was last generated on `r Sys.Date()`


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "TODO: ADD DIRECTORY PATH HERE")

library(data.table)
```

## Load Patent Table
```{r, warning=FALSE }
patent <- fread("G:/PatentsView/misc_filecounts/patent.tsv")
colnames(patent)[colnames(patent)=="type"] <- "patent_type"
colnames(patent)[colnames(patent)=="country"] <- "patent_country"
colnames(patent)[colnames(patent)=="id"] <- "patent_id"
head(patent)
```

## Load Assignee and Location Tables
```{r}
assignee <- fread("assignee.tsv")
location <- fread("location.tsv")

```
```{r}
head(assignee)
head(location)

```

## Load Raw Location and Raw Assignee Tables
```{r, warning=FALSE}

rawassignee <- fread("rawassignee.tsv")
rawlocation <- fread("rawlocation.tsv")

```
```{r}
head(rawassignee)
head(rawlocation)
```

## Join Raw Assignee and Assignee Tables
```{r}
merged_assignees <- merge(rawassignee, assignee, by.x = c('assignee_id', 'type', 'name_first', 'name_last', 'organization'), by.y = c('id','type', 'name_first', 'name_last', 'organization'))
```

```{r}
colnames(merged_assignees)[colnames(merged_assignees)=="type"] <- "assignee_type"

head(merged_assignees)

n_non_matches <- nrow(rawassignee) - nrow(merged_assignees)

```

The assignee table contains `r nrow(assignee)` rows while the rawassignee table contains `r nrow(rawassignee)` rows. The merging of these tables results in a table with `r nrow(merged_assignees)` rows. Thus there are `r n_non_matches` rows in the rawassignee table which do not contain matches to the assignee table on the specified columns.

## Join Raw Location and Location Tables
```{r}
head(location)
```

```{r}
colnames(rawlocation)[colnames(rawlocation)=="id"] <- "rawlocation_id"
head(rawlocation)
```


```{r}
merged_locations <- merge(rawlocation, location, by.x = c('location_id', 'city', 'state', 'country'), by.y = c('id','city', 'state', 'country'))
```



```{r}
head(merged_locations)

n_non_matches <- nrow(rawlocation) - nrow(merged_locations)

```


The location table contains `r nrow(location)` rows while the rawlocation table contains `r nrow(rawlocation)`rows. Merging these tables results in a merged_locations table of `r nrow(merged_locations)` rows. Thus there are `r n_non_matches` rows in the rawlocation table which do not have a matching location_id, city, state, and country in the location table.

## Join Merged_Locations and Merged_Assignees
```{r}
merged_assignee_location <- merge(merged_locations, merged_assignees, by.x = 'rawlocation_id', by.y = 'rawlocation_id')
```

```{r}
colnames(merged_assignee_location)[colnames(merged_assignee_location)=="type"] <- "assignee_type"
head(merged_assignee_location)
```

## Join Assignee, Location, and Patent Data
```{r}

head(patent)
```

```{r}
# free up some memory for final merge
rm(rawassignee)
rm(rawlocation)
rm(assignee)
rm(location)
rm(merged_locations)

complete_merge <- merge(patent, merged_assignee_location, by.x = 'patent_id', by.y = 'patent_id' )
```

```{r}
head(complete_merge)
```

The merged_assignee_location table contains `r nrow(merged_assignee_location)` rows and the patent table contains `r nrow(patent)`. The complete_merge contains `r nrow(complete_merge)` rows. Thus, all of the patent_ids in the merged_assignee_location table have matches in the patent table.

