---
title: "Merge Inventor, Location, and Patent Tables"
output: html_document
---

#### Note: This HTML document was last generated on `r Sys.Date()`


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "TODO: Add Directory Path Here")

library(data.table)
library(scales)
```

## Load Patent Table
```{r, warning=FALSE}
patent <- fread("patent.tsv")
colnames(patent)[colnames(patent)=="type"] <- "patent_type"
colnames(patent)[colnames(patent)=="country"] <- "patent_country"
colnames(patent)[colnames(patent)=="id"] <- "patent_id"
head(patent)

```

## Load Inventor and Location Tables
```{r, warning=FALSE}

inventor <- fread("inventor.tsv")
location <- fread("location.tsv")

```

```{r}
head(inventor)
head(location)

```

## Load Raw Inventor and Raw Location Tables
```{r, warning=FALSE}
rawinventor <- fread("rawinventor.tsv")
rawlocation <- fread("rawlocation.tsv")

```

```{r}
head(rawinventor)
colnames(rawlocation)[colnames(rawlocation)=="id"] <- "rawlocation_id"
head(rawlocation)

```

## Join Raw Location and Location Tables
```{r}
merged_locations <- merge(rawlocation, location, by.x = c('location_id', 'city', 'state', 'country'), by.y = c('id','city', 'state', 'country'))
```

```{r}
head(merged_locations)

n_non_matches <- nrow(rawlocation) - nrow(merged_locations)
```


The location table contains `r comma_format()(nrow(location))` rows while the rawlocation table contains `r comma_format()(nrow(rawlocation))` rows. Merging these tables results in a merged_locations table of `r comma_format()(nrow(merged_locations))` rows. Thus there are `r comma_format()(n_non_matches)` rows in the rawlocation table which do not have a matching location_id, city, state, and country in the location table.

## Join Raw Inventor and Inventor Tables
```{r}
# free up some memory 
rm(location)
rm(rawlocation)

```

```{r}
head(inventor)
```

```{r}
head(rawinventor)
```

```{r}
merged_inventors <- merge(rawinventor, inventor, by.x = c('inventor_id', 'name_first', 'name_last'), by.y = c('id', 'name_first', 'name_last'))
```

```{r}

head(merged_inventors)
n_non_matches <- nrow(rawinventor) - nrow(merged_inventors)
```

The inventor table contains `r comma_format()(nrow(inventor))` rows while the rawinventor table contains `r comma_format()(nrow(rawinventor))` rows. The resulting merged_inventors table contains `r comma_format()(nrow(merged_inventors))` rows. Thus there are `r comma_format()(n_non_matches)` rows in the rawinventor table which do not contain matching inventor_ids, first names, and last names in the inventor table.

## Join Merged_Inventors and Merged_Locations
```{r}
# free up some memory
rm(inventor)
rm(rawinventor)
```

```{r}
merged_inventor_location <- merge(merged_inventors, merged_locations, by.x = 'rawlocation_id', by.y = 'rawlocation_id')
```


```{r}
head(merged_inventor_location)
n_non_matches <- nrow(merged_locations) - nrow(merged_inventor_location)
```

The merged_locations table contains `r comma_format()(nrow(merged_locations))` rows, while the merged_inventors table contains `r comma_format()(nrow(merged_inventors))` rows. The resulting merge of these to tables contains `r comma_format()(nrow(merged_inventor_location))` rows. Thus, there are `r comma_format()(n_non_matches)` rows in the merged_locations table that are not matched by rawlocation_id in the merged_inventors table.

```{r}
rm(merged_inventors)
rm(merged_locations)

```


```{r}
head(patent)
```

## Join Inventor, Location, and Patent Data
```{r}
complete_merge <- merge(patent, merged_inventor_location, by.x = c('patent_id'), by.y = c('patent_id'))
```

```{r}
head(complete_merge)
```

The merged_inventor_location table contains `r comma_format()(nrow(merged_inventor_location))` rows and the patent table contains `r comma_format()(nrow(patent))` rows. The complete_merge contains `r comma_format()(nrow(complete_merge))` rows. Thus, all of the patent_ids in the merged_inventor_location table have matches in the patent table.